Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
\textit{i.e.} -> \ie (not italic)

The proposed approach is motivated in Section \ref{sec:motivations} and a brief review the state of the art in the field of acoustic scene modeling is given in Section \ref{sec:soa}. Then, the contributions are extensively described in Section \ref{sec:scattering} and \ref{sec:object}, respectively. Experiments carried out in an unsupervised setting, \textit{i.e.} acoustic scene similarity (ASS) and in a supervised setting, \textit{i.e.}  acoustic scene classification (ASC) are subsequently reported in Section \ref{sec:experiments}.

>>>>

The proposed approach is motivated in Section \ref{sec:motivations} and a brief review the state of the art in the field of acoustic scene modeling is given in Section \ref{sec:soa}. Then, the contributions are extensively described in Section \ref{sec:scattering} and \ref{sec:object}, respectively. Experiments carried out in an unsupervised setting, \ie acoustic scene similarity (ASS) and in a supervised setting, \ie acoustic scene classification (ASC) are subsequently reported in Section \ref{sec:experiments}.
